\documentclass[
  % Babel language, also used to load translations
  german,
  % Use A4 paper size, you can change this to eg. letterpaper if you need
  % the letter format. The normal methods to modify the paper size should
  % be picked up by SDAPS automatically.
  % a4paper, % setting this might break the example scan unfortunately
  % letterpaper
  %
  % If you need it, you can add a custom barcode at the center
  globalid=Inventionate,
  %
  % And the following adds a per sheet barcode at the bottom left
  print_questionnaire_id,
  %
  % You can choose between twoside and oneside. twoside is the default, and
  % requires the document to be printed and scanned in duplex mode.
  oneside,
  %
  % QR Codes instead Barcodes
  % style=qr,
  % The following options make sense so that we can get a better feel for the
  % final look.
  pagemark,
  stamp]{sdaps}
\usepackage[utf8]{inputenc}
\usepackage{multicol}

%############ SPEZIELLE FRAGEBOGENASAPTIONEN AUSGEHEND VON DER M.A. ############%

%%% SCHRIFTARTEN %%%
% Überschriften auf Helvetica setzen.
\usepackage[scaled]{helvet}
% KOMAScript Schriftarten setzen.
\setkomafont{choicefont}{\sffamily}
\setkomafont{marklinequestionfont}{\sffamily}
% Schriftart global auf Sans Serif setzen.
\renewcommand{\familydefault}{\sfdefault}


%%% FARBEN %%%
% Farbe der Fragebogenabschnitte ändern
\definecolor{sectionbgcolor}{rgb}{0.9,0.9,0.9}


%%% LAYOUT ANPASSUNG %%%
% Trennstrich zwischen den einzelnen Fragen
\newcommand{\seperate}[1][0.3]{\vspace{#1cm}\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}}\vspace{#1cm}}


\author{Fabian Mundt}
\title{Zeit-Raum Studium --- Fragebogen I}

\begin{document}
  % Everything you do should be done inside the questionnaire environment.

  % If you don't like the default text at the beginning of each questionnaire
  % you can remove it with the optional [noinfo] parameter for the environment
  \begin{questionnaire}
    % There is a predefined "info" style to hilight some text.
    \begin{info}
	Sehr geehrte Studentinnen und Studenten,\\

	der folgende Fragebogen bezieht sich auf Studienvoraussetzungen von StudienanfänerInnen des Lehramts an der Pädagogischen Hochschule Karlsruhe. Die Erhebung und Auswertung findet im Rahmen meiner Masterarbeit \textit{»Viel dahinter --- viel vor« Eine Sozioanalyse von StudienanfängerInnen des Lehramts an der Pädagogischen Hochschule Karlsruhe} statt.

	\vspace{.5em}

	Ich bitte Sie, sich Zeit zu nehmen und den Fragebogen ehrlich und vollständig zu bearbeiten. Die Auswertung erfolgt anonym und wird nicht auf Sie persönlich rückführbar sein.

	\vspace{.5em}

	Ihre Antworten helfen mir weiter, die komplexe Lage zu Beginn des Studiums besser verstehen zu lernen. Dieses tiefere Verständnis soll letztlich auch Ihnen helfen, indem es ganz konkret auf die Verbesserung der Studienbedingungen vor Ort abzielt.

%\\{\bf Bitte beachten Sie, dass der Fragebogen zweiseitig bedruckt ist und die Fragen immer durch Trennlinien voneinander abgegrenzt sind.}\\

	\vspace{.5em}

	Vielen Dank im Voraus für Ihre Bereitschaft, Hilfe und Unterstützung!

    \end{info}

    % Use \addinfo to add metadata (which is printed on the report later on)
    \addinfo{Date}{10.03.2013}

    % You can structure the document using sections. You should not use
    % subsections yourself, as these are used to typeset question text.
    \section{Fragen zu Ihrer Person}

	\begin{choicequestion}[6]{Wann wurden Sie geboren?}
        \choiceitemtext{1cm}{1}{\hspace{2cm}Monat:}
        \choiceitemtext{1cm}{2}{Jahre:}
    \end{choicequestion}

    \seperate

    \begin{choicequestion}[1]{Welches biologische Geschlecht haben Sie?}
         \choiceitem{Männlich}
         \choiceitem{Weiblich}
    \end{choicequestion}

    \seperate

   \setcounter{markcheckboxcount}{7}

   \singlemark{What do you think of this LaTeX class?}{nothing}{looks great}

   \seperate

   \setcounter{markcheckboxcount}{10}

    % Now we would like to ask multiple range questions that are similar. We
    % can use a markgroup environment to typeset many range questions under
    % one heading.
    \begin{markgroup}{What do you think about the following aspects of \LaTeX?}
      \markline{equation syntax}{bad}{good}
      \markline{rendered equations}{ugly}{beautiful}
      \markline{ease of use}{hard}{easy}
    \end{markgroup}

    \section{Choice Questions}
    We can also give users a question with predefined choices. Such a list
    of choices is typesetted using a tabularx environment with equally
    sized columns. Items can span multiple columns.

    \begin{choicequestion}[3]{Which of the following Open Source
                              Optical Mark Recognition software
                              packages have you heard about?}
      \choiceitem{SDAPS}
      \choicemulticolitem{2}{Auto Multiple Choice}
      \choiceitem{QueXF}

      % Insert a text field. The freeform box automatically scales horizontally
      % The first parameter is the height of the box. The second parameter
      % is the amount of columns it should span.
      \choiceitemtext{1.2cm}{2}{Other:}
    \end{choicequestion}

    \seperate

    % And a more compact way of doing it; similar to markgroup
    \begin{choicegroup}{Which software do you prefere for the following tasks?}
      % We have to add the possible choices at the start.
      \groupaddchoice{\LaTeX}
      \groupaddchoice{LibreOffice}
      \groupaddchoice{Microsoft Word}
      \groupaddchoice{other}

      % After that it is possible to add each question.
      \choiceline{writing letters}
      \choiceline{creating tables}
      \choiceline{typesetting equations}
    \end{choicegroup}

    \section{Freeform text fields}

    SDAPS will extract freeform textfields such as below as images and put
    these into reports. SDAPS knows whether there is writing in the box and
    how large it is.

    % This is a textbox which is at least 2cm high. It will automatically scale
    % to fill the page.
    \textbox{2cm}{Do you have any comments?}

    % Force a new page here
    \newpage
    \section{Tricks and Features}
    SDAPS can also use circular checkboxes if you prefere. Or you can use the
    {\tt multicol} package to create multi-column layouts as is done below.

    % Set checkbox style to be circular
    \def\checkboxstyle{ellipse}

    \begin{multicols}{2}
      \singlemark{This is a range question}{lower bound}{upper bound}%
      % Note that we need the % at the end of the last line to prevent
      % LaTeX from inserting too much whitespace.
      \label{somelabel}

      As you can see, this is a multi-column layout. The {\tt markgroup} and
      {\tt choicegroup} environments may be a bit tight in this mode.

      Lets put some more questions here, just because we can.

      \begin{choicequestion}[1]{A choice question!}
        \choiceitem{first choice}
        \choiceitem{second choice}
        \choiceitem{third choice}
        \choiceitemtext{1.2cm}{1}{other:}
      \end{choicequestion}

      \singlemark{Another range question}{lower bound}{upper bound}
      This text is closer to the question compared to question~\ref{somelabel}
      because it is not starting a new paragraph.


      \textbox{3cm}{And a freeform text field}
    \end{multicols}

    That's it for the multi-column part; it was fun while it lasted!

    There are some more special commands. You can draw \checkedbox{} crossed
    checkboxes, \filledbox{} filled or \correctedbox{} filled and crossed ones. Finally there is
    also the plain \checkbox*{} checkbox using {\tt \textbackslash{}checkbox*}.

    \textbox*{2cm}{And textboxes with a fixed height. This one is exactly 2\,cm high.}

    % Reset checkbox style again.
    \def\checkboxstyle{box}

  \end{questionnaire}
\end{document}
